\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-18 paper/paper.Rnw
fixes to syntax, update TODO

powercoef <- read.csv("sas/PowerEstimates.csv")
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
kable(powercoef[1:6,], format="latex", digits=2, caption="Main Effects")
kable(powercoef[7:12,], format="latex", digits=2, caption="Interaction Effects")
@
\end{table}

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='powerfit', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE>>=
rabs <- seq(0,0.9,0.02)
t <- c(12, 24, 48, 96)
#pred <- data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), plot=c(0,1),
#                                      subj_id=full.sub$subj_id))
#write.csv(pred, "sas/predgrid.csv") # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
prediction <- read.csv("sas/predfit.csv") #Large file, very slow
colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "plot", "subj_id", "weights", "detected", "RandomEf", "FixedEf", "residual")
glmm.resid <- subset(prediction, detected==0 | detected==1)
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), plot = ifelse(plot==1, "Overlaid Lines", "Scatterplot"), plot = ifelse(smoothed==1, paste(plot, "(Smoothed)", sep=" "), plot))
prediction <- select(prediction, rabs, t, rsgn, smoothed, plot, subj_id, RandomEf, FixedEf)
prediction <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))

>>>>

powercoef <- read.csv("sas/PowerEstimates.csv")
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
kable(powercoef[1:6,], format="latex", digits=2)
kable(powercoef[7:12,], format="latex", digits=2)
@
\end{table}

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='powerfit', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE>>=
rabs <- seq(0,0.9,0.02)
t <- c(12, 24, 48, 96)
#pred <- data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), plot=c(0,1),
#                                      subj_id=full.sub$subj_id))
#write.csv(pred, "sas/predgrid.csv") # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
prediction <- read.csv("sas/predfit.csv") #Large file, very slow
colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "plot", "subj_id", "weights", "detected", "Included", "RandomEf", "FixedEf", "residual")
glmm.resid <- subset(prediction, detected==0 | detected==1)
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), plot = ifelse(plot==0, "Overlaid Lines", "Scatterplot"), plot = ifelse(smoothed==1, paste(plot, "(Smoothed)", sep=" "), plot))
prediction <- select(prediction, r, t, rsgn, smoothed, plot, subj_id, RandomEf, FixedEf)
prediction <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))
